\documentclass[english]{thesis}
%\includeonly{intro}
\title{Some microlocal aspects of perverse coherent sheaves and equivariant D-modules}
\author{Clemens Koppensteiner}
\version{0}

\usepackage{math-alg,math-ag, math-gl}

\addbibresource{global.bib}
%\bibliography{global.bib}

\input{macros}

\begin{document}

\frontmatter

\maketitlepage

\begin{abstract}
    We discuss microlocal aspects of two types of sheaves which are of interest to geometric representation theory: perverse coherent sheaves and equivariant D-modules.

    The category of perverse sheaves on a complex variety is characterized by exactness of the microlocal stalks (or vanishing cycles) functor.
    We prove an analogue of this characterization for the category of perverse coherent sheaves on a scheme with a group action.
    The main idea is to understand microlocal stalks via local cohomology along half-dimensional (\enquote{Lagrangian}) subvarieties.
    We define \enquote{measuring subvarieties} as an analogue of these subvarieties in the coherent setting and show how they can be used to characterize perverse coherent sheaves.

    The second part of this thesis is dedicated to understanding the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of equivariant D-modules.
    We discuss how to compute the Hochschild cohomology of the category of D-modules on a quotient stack via a relative compactification of the diagonal morphism.
    We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
\end{abstract}

\include{acknowledgments}

\tableofcontents

\mainmatter

\include{intro}
\include{perverse-coherent}
\include{d-mod}

\backmatter

\printbibliography

\end{document}
